Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
Update paper.tex

\if{false}
As an example use-case, ZLog needs to
store metadata information with each object so for each operation, it
checks the epoch value and write capability (2 metadata reads) and
writes the index (metadata write).
\fi

For example, Figure~\ref{fig:datavsxattr} compares the throughput
(\emph{y} axis) over time (\emph{x} axis) of two OSD implementations of the same storage object interface for
storing metadata: either in the header of the byte stream (data) or in the
object extended attributes (XATTR). The speed for appending data without
any metadata operations (data raw) is also shown as a baseline for
comparison. For append-heavy workloads storing metadata as a header in
the data performs about 1.5x better than storing metadata as an extended
attribute.

@@

The object interface facility provided by Ceph is more than an
a proof-of-concept active storage implementation.  Figure~\ref{fig:obj-int-dev-growth} shows a dramatic growth in the production use of
domain-specific interfaces in the Ceph community since 2010.  What is most
remarkable is that this trend contradicts the notion that API changes are a
burden for users.
Rather it appears that a gap in existing interfaces are
being addressed through programmability. In fact, Table~\ref{table:objclasses}
categorizes existing interfaces and we clearly see a trend towards reusable
services.

@@

A consistent view of cluster state among Ceph daemons and clients is critical
to provide strong consistency guarnatees to clients.  Ceph maintains cluster
state information in per-subsystem ``maps'' (e.g. OSD map, MDS map) that
record membership and status information. A PAXOS-based monitoring service is
responsible integrating state changes into cluster maps, and responding to
requests from out-of-date clients.  As a fundamental building block of many
system designs, consensus abstractions such as PAXOS are a common technique
for maintaining consistent data versions, and are a useful system to expose.
While Ceph does not expose this service directly, it does allow limited use by
clients through a key-value service intended for low-volume, small size
configuration information.

@@

Ceph provides storage by striping and replicating data across
RADOS~\cite{weil_rados_2007}, the reliable distributed object store. RADOS
uses many techniques to ensure that data is not corrupted or lost, such as
erasure coding, replication, and data scrubbing. Furthermore, many of these
techniques try to be autonomous so that work is distributed across the
cluster. For example, when placement groups change the OSDs rebalance and
re-shard data in the background in a process called placement group splitting.

>>>>

\if{false}
As an example use-case, ZLog needs to
store metadata information with each object, so for each operation, it
checks the epoch value and write capability (2 metadata reads) and
writes the index (metadata write).
\fi

For example, Figure~\ref{fig:datavsxattr} compares the throughput
(\emph{y} axis) over time (\emph{x} axis) of two OSD implementations of the same storage object interface for
storing metadata: either in the header of the byte stream (data) or in the
object extended attributes (XATTR). The speed for appending data without
any metadata operations (data raw) is also shown as a baseline for
comparison. For append-heavy workloads, storing metadata as a header in
the data performs about 1.5x better than storing metadata as an extended
attribute.

@@

The object interface facility provided by Ceph is more than
a proof-of-concept active storage implementation.  Figure~\ref{fig:obj-int-dev-growth} shows a dramatic growth in the production use of
domain-specific interfaces in the Ceph community since 2010.  What is most
remarkable is that this trend contradicts the notion that API changes are a
burden for users.
Rather it appears that a gap in existing interfaces are
being addressed through programmability. In fact, Table~\ref{table:objclasses}
categorizes existing interfaces and we clearly see a trend towards reusable
services.

@@

A consistent view of cluster state among Ceph daemons and clients is critical
to provide strong consistency guarantees to clients.  Ceph maintains cluster
state information in per-subsystem ``maps'' (e.g. OSD map, MDS map) that
record membership and status information. A PAXOS-based monitoring service is
responsible for integrating state changes into cluster maps, and responding to
requests from out-of-date clients.  As a fundamental building block of many
system designs, consensus abstractions such as PAXOS are a common technique
for maintaining consistent data versions, and are a useful system to expose.
While Ceph does not expose this service directly, it does allow limited use by
clients through a key-value service intended for low-volume, small size
configuration information.

@@

Ceph provides storage by striping and replicating data across
RADOS~\cite{weil_rados_2007}, the reliable distributed object store. RADOS
uses many techniques to ensure that data is not corrupted or lost, such as
erasure coding, replication, and data scrubbing. Furthermore, many of these
techniques try to be autonomous so that work is distributed across the
cluster. For example, when placement groups change, the OSDs rebalance and
re-shard data in the background in a process called placement group splitting.
